Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-28 bbbq_article.tex
EOD

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EpitopePrediction versus MHCnuggets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

EpitopePrediction is a recent tool, used in \cite{bianchi2017},
and can predict MHC-I epitopes.
MHCnuggets is an even newer tool to predict both MHC-I and MHC-II epitopes.

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ep_vs_mhcn/ep_vs_mhcn.png}
  Predicted IC50 (in nM) for EpitopePrediction and MHCnuggets
  \caption{
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{fig:ep_vs_mhcn}
\end{figure}

\begin{table}[!htbp]
  \input{ep_vs_mhcn/ep_vs_mhcn.latex}
  \caption{
    Correlation coefficients for different haplotypes
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{table:ep_vs_mhcn}
\end{table}
